% Created 2023-04-01 Sat 13:35
% Intended LaTeX compiler: pdflatex
\documentclass[14pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{minted}
\usepackage[utf8x]{inputenc}
\usepackage{minted}
\usepackage[T2A]{fontenc}
\usepackage[russian]{babel}
\usepackage{tempora}
\usepackage{geometry}
\geometry{a4paper, left=30mm, top=20mm, bottom=20mm, right=15mm }
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{float}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{titlesec}
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}
\titleformat*{\subsubsection}{\normalsize\bfseries}
\addto\captionsrussian{\renewcommand{\contentsname}{\centering \normalsize СОДЕРЖАНИЕ}}
\addtocontents{toc}{\protect\thispagestyle{empty}}
\usepackage{titletoc}
\titlecontents{section}[0pt]{}{\contentsmargin{0pt} \thecontentslabel\enspace}{\contentsmargin{0pt}}{\titlerule*[0.5pc]{.}\contentspage}[]
\dottedcontents{subsection}[6.1em]{}{3.2em}{.5pc}
\author{Панков Вася}
\date{\today}
\title{Тестовый пример}
\hypersetup{
 pdfauthor={Панков Вася},
 pdftitle={Тестовый пример},
 pdfkeywords={},
 pdfsubject={Всё что я здесь пишу, нужно для теста.},
 pdfcreator={Emacs 30.0.50 (Org mode 9.6.2)}, 
 pdflang={Russian}}
\begin{document}

\begin{titlepage}

\centering{ГУАП}

\vspace{32pt}

\centering{ФАКУЛЬТЕТ СРЕДНЕГО ПРОФЕССИОНАЛЬНОГО ОБРАЗОВАНИЯ}

\vspace{60pt}

\raggedright{ОТЧЕТ \\
ЗАЩИЩЕН С ОЦЕНКОЙ}
\vspace{14pt}

\raggedright{ПРЕПОДАВАТЕЛЬ}

\vspace{12pt}

\begin{tabularx}{\textwidth}{ >{\centering\arraybackslash}X >{\centering\arraybackslash}X >{\centering\arraybackslash}X }
	 преподаватель & & Всё что я здесь пишу, нужно для теста. \\ 
	 \hrulefill & \hrulefill & \hrulefill \\ 
\footnotesize{должность, уч. степень, звание} & \footnotesize{подпись, дата} & \footnotesize{инициалы, фамилия} \\ 
\end{tabularx} 
 
\vspace{48pt} 

\centering{ОТЧЕТЫ О ЛАБОРАТОРНЫХ РАБОТАХ} 

\vspace{76pt} 

\centering{По дисциплине: Тестовый пример} 

\vspace*{\fill} 

\raggedright{РАБОТУ ВЫПОЛНИЛ} 

\vspace{10pt} 

\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}X  >{\centering\arraybackslash}X >{\centering\arraybackslash}X >{\centering\arraybackslash}X }
	 СТУДЕНТ ГР. № & 021к & & Панков Вася \\ 
	 & \hrulefill & \hrulefill & \hrulefill \\ 
	 &  & \footnotesize{подпись, дата} & \footnotesize{инициалы, фамилия} \\ 
\end{tabularx} 
 
\vspace*{\fill} 

\centering{Санкт-Петербург \the\year} 

\end{titlepage}

\tableofcontents \clearpage

\section{Кто я такой?}
\label{sec:org26625fd}

Я Искуственный интелект, который пишет этот ненужный текст.

$$ 2 + 2 = 5 $$

\section{Have you ever solved a conflict? What is your position when you see a conflict in the organisation?}
\label{sec:org391f723}


Yes, I have dealt with conflicts. Anything can be source of conflicts,
but many conflicts happened with tired people. And I believe that if
you give two sides rest, it can helped to resolve conflict. But not all
conflicts occur with 

TESTSTSTSTSTSTSTSTESTSE
\end{document}